Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-07-03 intro.tex
Modificada Introduccion

In this work, we compare five machine learning techniques to predict
the development rate of the black Sigatoka disease: support vector
regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression,
using input variables such as \review{completar las variables de
  entrada usada} to predict \review{completar las variables de salida}.

\todofn{The main contribution of this work}%
{Definitivamente ese no es el aporte principal del artículo.  Cuando
  esté listo el resto hay que volver aquí.  Creo que va a ser algo
  como mostrar la relevancia de la etapa de preprocesamiento, o
  mostrar que a pesar de ser sistemas complejos, con variables
  caóticas, lo mejor en este caso son predictores lineales, o algo por
  el estilo.} %
% 
 is the selection of the best machine learning technique
to forecast the black Sigatoka development rate according to the
metric indicated below.

>>>>

In this work, we compare five machine learning techniques to predict
the development rate of the black Sigatoka disease: support vector
regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression,
using input variables such as: air temperature, relative humidity, solar radiation, precipitation and wind speed \review{completar las variables de
  entrada usada - Modificado} to predict the evolution stage in the biological warning system\review{completar las variables de salida - Modificado}.

\todofn{The main contribution of this work}%
{Definitivamente ese no es el aporte principal del artículo.  Cuando
  esté listo el resto hay que volver aquí.  Creo que va a ser algo
  como mostrar la relevancia de la etapa de preprocesamiento, o
  mostrar que a pesar de ser sistemas complejos, con variables
  caóticas, lo mejor en este caso son predictores lineales, o algo por
  el estilo - Pendiente} %
% 
 is the selection of the best machine learning technique
to forecast the black Sigatoka development rate according to the
metric indicated below.
